\chapter{Introduction to TeXstudio}

\section{What is LaTeX ?}

\huge LaTeX, \normalsize {which is a shortening of Lamport TeX\footnote[1]{ TeX is a typesetting system (or "formatting system") designed and mostly written by Donald Knuth and released in 1978. TeX was designed to allow anybody to produce high-quality books using minimal effort, and to provide a system that would give exactly the same results on all computers, at any point in time.}
	, is a document preparation system. Unlike formatted text, as Microsoft Word, LaTeX is a plain text, which in it the writer uses markup tags to define the structure of a document (such as book, letter and article), as well as the style of text and the whole document in general.
\\According to that, LaTeX encourages authors to focus on their content, not on the appearance or format of it.
\\A TeX distribution such as TeX Live or MikTeX is used to produce an output file (such as PDF) suitable for printing or digital distribution.}

\clearpage

\section{A Simple document}

\subsection{Create a document}
The first step in your document, is to define its type : \\
$\backslash$documentclass\{Type\}
\\This type could be : article, book, beamer (presentation slide show), ...etc.
\\Or you can use the existed templates in TeXstudio by going to file $\rightarrow$ New from template, and choose your desired one.

\subsection{Main-Page Content}
As any document must have a title, an author and a date of creation. you can add them by following these steps :
\\

$\backslash$title\{The document Title\}

$\backslash$author\{Your Name\}

$\backslash$date\{date\},\\if you didn't write one,the current date will be added automatically.
\\

Then you have to create the main-page, which'll be formatted on its own, to be a different one.

$\backslash$frontmatter

$\backslash$maketitle
\\


And then, you can finally Start Your Actually Document!\\

$\backslash$begin\{document\}

First document. Type your document text here.

$\backslash$end\{document\}
\clearpage

\section{Document Structure}
\subsection{Table of Contents}

If you want to add a table of the contents of your document, you can simply add it by using :
\\

$\backslash$tableofcontents
\\It'll be organized automatically depending on the chapters, sections and subsections you wrote.

\subsection{Chapters, Sections and Subsections}

